---
title: "HW 1"
author: "Alice Gee"
date: "8/26/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
1) Combing with c
  A. "character"
  B. "character"
  C. "list" 
  D. "numeric" 
  E. "list"
  F. 8
  G. 5
  H. 4
  I. 1, This is different from the answer in part H because 
    [1] is refering for a single item in the vector. In part H, 
    we are counting all the items in wal and one item from rus. 

2) Hypotenuse 
  hypotenuse = function (a, b) {
  c = sqrt(a^2 + b^2)
  return(c)
  }
  
3) Overlapping intervals
  A. 
    overlap = function(g,h) {
      if (g[1] > h[1] & g[1] < h[2]) {
        return(TRUE)
      } else if (h[1] > g[1] & h[1] < g[2]) {
        return(TRUE)
      } else if (g[1] == h[1]) {
        return(TRUE)
      } else {
        return(FALSE)
      }
    }
  B. TRUE, There is a between g and h since g[1] (200) is in 
  the range of h[1] (100) and h[2] (250). There is an overlap 
  of approximately 50. 
  C. FALSE, The given intervals have no overlap. 
  
4. Fun with functions
  4.1 Powers of f0
    A. 5
    B. 7
    C. The function f1(2) takes 2 as the argument for x and
    returns the function functionalPower(f0, y). The output would
    essentially be f1(2) = 2 + y. 
    D.`%op1%` = function(x, y) {f1(x)(y)} is an operator
    defined function that takes in arguments x and y, and applies
    them to the f1 function that was previously defined. x %op1% y 
    represents a different method of calling f1(x)(y), in that it
    also takes in the two arguments of x and y and adds them together.
    x + y
    
  4.2 Powers of f1
    A. 6
    B. 12
    C. The function f2(2) takes 2 as the argument for x and
    returns the function functionalPower(f1(x), y-1). The output
    of f2(2) = 2 * y, since the f2 function multiplies the x and 
    y arguments together. 
    D. `%op1%` = function(x, y) {f2(x)(y)} is an operator 
    defined function that takes in arguemnts x and y, and applies them 
    to the f2 function that was previously defined. x %op2% y 
    represents a different method of calling f2(x)(y), in that it 
    also takes in the two arguments of x and y and multiplies them
    together. 
    x * y 
  
  4.3 Powers of f2
    A. 8
    B. 81
    C. The function f3(2) takes 2 as the argument for x and
    returns the function functionalPower(f2(x), y-1). The output
    of f3(2) = 2 ** y (or 2 ^ y). 
    D. `%op1%` = function(x, y) {f3(x)(y)} is an operator 
    defined function that takes in arguemnts x and y, and applies them 
    to the f3 function that was previously defined. x %op2% y 
    represents a different method of calling f3(x)(y), in that it 
    also takes in the two arguments of x and y and raises x to the 
    power of y. 
    x ** y or x ^ y


```{r}
wal = c(c(1, 2, 3), "string")
class(wal)
class(wal[[1]])
rus = c(list(1, 2, 3), "string")
class(rus)
class(rus[[1]])
class(c(wal, rus))
length(c(wal, rus))
length(c(list(wal), rus))
length(c(list(wal), rus)[[1]])
length(c(list(wal), rus)[1])

hypotenuse = function (a, b) {
  c = sqrt(a^2 + b^2)
  return(c)
}
hypotenuse(3, 4)

overlap = function(g,h) {
  if (g[1] > h[1] & g[1] < h[2]) {
    return(TRUE)
  } else if (h[1] > g[1] & h[1] < g[2]) {
    return(TRUE)
  } else if (g[1] == h[1]) {
    return(TRUE)
  } else {
    return(FALSE)
  }
}

overlap(g=c(200, 400), h=c(100, 250))
overlap(c(500, 600), c(800, 900))

f0 = function(x) {x +1}

functionalPower = function(f, power) { 
  fRepeatedPowerTimes = function(x) {
    if (power == 0) {
      return(x)
    } else {
      for (i in 1:power) {
        x = f(x)
      }
    }
    return(x)
  }
  return(fRepeatedPowerTimes)
}

f1 = function(x) {
  return(function(y) {
    f0_to_y = functionalPower(f0,y)
    return(f0_to_y(x))
  })
}
f1(2)(3)
f1(3)(4)

`%op1%` = function(x, y) {f1(x)(y)}
2 %op1% 3

f2 = function(x) {
  return(function(y) {
    f1ofx_to_yminus1 = functionalPower(f1(x), y-1)
    return(f1ofx_to_yminus1(x))
  })
}

f2(2)(3)
f2(3)(4)

f3 = function(x) {
  return(function(y) {
    f2ofx_to_yminus1 = functionalPower(f2(x), y-1)
    return(f2ofx_to_yminus1(x))
  })
}
f3(2)(3)
f3(3)(4)
      
```

