---
title: "HW 4"
author: "Alice Gee"
date: "9/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. 
```{r}
fixedSizeStepper = function(nSteps){
  sample(c(-1,+1), nSteps, replace = TRUE)
}

uniformStepper = function(nSteps){
  sqrt(12) * (runif(nSteps)-1/2)
}

randomWalk = function(nSteps, stepper) {
  steps = stepper(nSteps)
  return(c(0,cumsum(steps)))
}
```
2. 
```{r}
randomWalks = function(nSteps, stepper = fixedSizeStepper, nWalks = 100000) {
  lapply(1:nWalks, function(i) {randomWalk(nSteps, stepper)})
}

fixedStepWalks <- randomWalks(nSteps = 100, stepper = fixedSizeStepper, nWalks = 100000)
unifWalks <- randomWalks(nSteps = 100 , stepper = uniformStepper, nWalks = 100000)
gaussianWalks <- randomWalks(nSteps = 100, stepper = rnorm, nWalks = 100000)
```
3. 
```{r}
positionsAtStepT = function(walks, t){
  unlist(lapply(walks, function(rw) {rw[[t+1]]}))
}

edit_positionAtStepT = function(walks, t){
  lapply(walks, function(rw) {rw[[t+1]]})
}

temp <- positionsAtStepT(fixedStepWalks, 5)
head(temp)
class(temp)
temp2 <- edit_positionAtStepT(fixedStepWalks, 5)
head(temp2)
class(temp2)
```
  A. The class of the object returned by positionAtStepT is a numeric. 
  B. Removing the unlist function returns the output of each value as an individual element in a list. 
  C. We use [[t+1]] in the code instead of [[t]] because we want to check the positions of the walker through the last step that they take. By using [[t+1]], we get the positions after we take step t, not the position we are at before we take step t.     
4. 
```{r}
plotData = lapply(c(1, 2, 5, 10), function(nSteps) {
  rbind(
    data.frame(stepper = "+/-1",      ## recycled
               t = nSteps,            ## recycled
               x = positionsAtStepT(fixedStepWalks, nSteps)),
    data.frame(stepper = "uniform",   ## recycled
               t = nSteps,            ## recycled
               x = positionsAtStepT(unifWalks, nSteps)),
    data.frame(stepper = "gaussian",  ## recycled
               t = nSteps,            ## recycled
               x = positionsAtStepT(gaussianWalks, nSteps))
  )
})
class(plotData)
length(plotData)
plotData = do.call(rbind, plotData)
class(plotData)
nrow(plotData)
ncol(plotData)
```
  A. The length of the first argument in lapply is 4. 
  B. The comments "recycled" indicates that we are reusing the same values [of nSteps] for each of the types of randomWalks methods to get the positions. In general, the recycled comment indicates that we are reusing methods of values.
  C. The class of plotData is a list. 
  D. The length of plotData is 4. 
  E. The class of plotData is now a data frame. 
  F. There are 1200000 rows and 3 columns in plotData. 
5. 
```{r}
library(ggplot2); theme_set(theme_bw())
gg = ggplot(plotData, aes(x=x))
## facet_grid splits the plot into a grid of panels (or facets)
## based on two categorical variables---here stepper and t,
## separated by a tilde (~)---with all data sharing the same
## combination of one value of stepper and one value of t
## plotted together in the appropriate facet of the grid:
gg = gg + facet_grid(stepper ~ t, scales="free_x")
## center=0 below tells histogram to center one of the bins on 0:
gg = gg + geom_histogram(center=0, fill="darkgray", color="darkslategray")
print(gg)
```
  A. Similar to fixedSizeStepper, uniformStepper and gaussianStepper both have a distribution similar to that of a normal distribution after many steps. For uniformStepper, we are picking a step size with uniform probability such that it yields a mean of 0 and a standard deviation of 1, which is similar to the sample distribution used in fixedSizeStepper. This results in a normal distribution type after many walks, in a similar nature to fixedSizeStepper. For guassianStepper, the function utilizes the built-in function in R that simulates a normal distribution with a [default] mean of 0 and a standard deviation of 1. These qualities allow the distribution to be consistently normal, regardless of the number of steps taken, which resembles the normal [approximated] distribution of fixedSizeStepper after many steps. 
  B. fixedSizeStepper can be distinguished from the other two methods in that fixedSizeStepper returns integer values since each step is chosen from +1 or -1, both of which are integers. For unifWalks and gaussianWalks, they both yield floats (decimal numbers) because the step values are chosen from [usually] non-integer numbers. 
```{r}
tail(fixedStepWalks[[1]])
tail(unifWalks[[1]])
tail(gaussianWalks[[1]])
```
